### 2020-03-08 papers.tex
Add papers received thus far

\addtrack
	{}{Gamification}
\addpaper
	{Aumann agreement by combat}
	{Travis Hance}
	{Keywords: Aumann agreement, combat, agents}
	{SIGBOVIK_2019_paper_18}
	{0cm}
	{}
\addpaper
	{Monetization of development tools for fun and profit}
	{Albin Eldstål-Damlin}
	{Keywords: monetization, micro-transactions, free-to-play, gamification}
	{SIGBOVIK_2019_paper_1}
	{0cm}
	{}
\addreview{SIGBOVIK_2019_review_1}{0cm}

\addtrack
	{}{Let's get this party started!}
\addpaper
	{Elo World: A framework for benchmarking weak chess engines}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: pawn, horse, bishop, castle, queen, king}
	{SIGBOVIK_2019_paper_41}
	{0cm}
	{\link{https://sf.net/p/tom7misc/svn/HEAD/tree/trunk/chess}}
\addpaper
	{A formal treatment of k/n power-hours}
	{Christian Clausen}
	{Keywords: power hour, 2 girls 1 cup, formalized drinking game}
	{SIGBOVIK_2019_paper_4}
	{0cm}
	{}
\addpaper
	{Eventually consistent partying}
	{Veit Heller}
	{Keywords: party system design, buzz factor, SIGBOVIK}
	{SIGBOVIK_2019_paper_17}
	{0cm}
	{}

\addtrack
	{}{Survival advice from a computer scientist}
\addpaper
	{Survival in chessland}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, chess to the death, being a chesspiece to the death}
	{SIGBOVIK_2019_paper_10}
	{0cm}
	{\link{https://sf.net/p/tom7misc/svn/HEAD/tree/trunk/chess}}
\addpaper
	{Optimizing \textit{The Sacrifice}}
	{Nico Zevallos}
	{Keywords: Tarkovsky, \textit{Offret}, film, movie, optimization, path planning, pursuit, evasion, art}
	{SIGBOVIK_2019_paper_13}
	{0cm}
	{}
\addpaper
	{Abusing the RPM package manager to compile software}
	{ILIANA DESTROYER OF WORLDS}
	{Keywords: Linux, software management, recursion}
	{SIGBOVIK_2019_paper_16}
	{0cm}
	{\link{https://github.com/amazonlinux/rust-bundled-packaging/tree/b9c50d16b6d517c4e7483c6842b6f3cc77969b9d}}

\addtrack
	{}{Security and privacy}
\addpaper
	{CVE-2018-90017117}
	{\texttt{t0m7}}
	{Keywords: kingme, exploit, input validation}
	{SIGBOVIK_2019_paper_3}
	{0cm}
	{}
\addpaper
	{Orchhit: User-oblivious social networking}
	{Jim McCann}
	{Keywords: privacy, hashing, cryptography}
	{SIGBOVIK_2019_paper_37}
	{0cm}
	{\link[Their system is live at:]{http://orchhit.com}}

\addtrack
	{}{Machine learning}
\addpaper
	{Color- and piece-blind chess}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, handicaps, man-in-the-middle attacks, neural networks}
	{SIGBOVIK_2019_paper_36}
	{0cm}
	{\link{https://sf.net/p/tom7misc/svn/HEAD/tree/trunk/chess/blind}}
\addpaper
	{Dimensionality-reducing encoding for classification of Pythagorean engendered numbers}
	{Rany Tith and Oscar I.\@ Hernandez}
	{Keywords: number theory, machine learning, encoding, information theory, classification, gender theory, integers, globalization, computation, mathematics}
	{SIGBOVIK_2019_paper_28}
	{0cm}
	{}
\addpaper
	{emojizip: A text compression system based on pictogram-kiloword equivalence}
	{William Gunther and Brian Kell}
	{Keywords: data compression, TensorFlow, [laughing crying emoji]}
	{SIGBOVIK_2019_paper_39}
	{0cm}
	{\link[The authors assure us the materials will be available ``if they get around to it'':]{http://zifyoip.com/emojizip}}
\addreview{SIGBOVIK_2019_review_39}{0cm}
\addpaper
	{Meta-meta-learning for neural architecture search through arXiv Descent}
	{Antreas Antoniou \textit{et al.}}
	{Keywords: meta, meta-meta, deep, NAS}
	{SIGBOVIK_2019_paper_11}
	{0cm}
	{}
\addpaper
	{Towards automatic low hanging fruit identification for the steering of ML research}
	{Nick Frosst and Aidan Gomez}
	{Keywords: machine learning, detection, segmentation, orientation, apple, akee, apricot, avocado, banana, bilberry, blackberry, blackcurrant, black sapote, blueberry, boysenberry, Buddha's hand (fingered citron), crab apples, currant, cherry, cherimoya (custard apple), chico fruit, cloudberry, coconut, cranberry, cucumber, damson, date, dragonfruit (or pitaya), durian, elderberry, feijoa, fig, goji berry, gooseberry, grape, raisin, grapefruit, guava, honeyberry, huckleberry, jabuticaba, jackfruit, jambul, japanese plum, jostaberry, jujube, juniper berry, kiwano (horned melon), kiwifruit, kumquat, lemon, lime, loquat, longan, lychee, mango, mangosteen, marionberry, melon, cantaloupe, honeydew, watermelon, miracle fruit, mulberry, nectarine, nance, olive, orange, blood orange, clementine, mandarine, tangerine, papaya}
	{SIGBOVIK_2019_paper_32}
	{0cm}
	{}

\addtrack
	{}{Architecture: Faster and hotter}
\addpaper
	{Turing-complete chess}
	{Ross Dempsey, Sydney Timmerman, Karl Osterbauer, and Kat Xiang}
	{Keywords: chess, automata, mahogany, Turing machine}
	{SIGBOVIK_2019_paper_26}
	{0cm}
	{}
\addpaper
	{NaN gates and flip FLOPS}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: IEEE 754, mathematics, universal computation, gentleNaN}
	{SIGBOVIK_2019_paper_42}
	{0cm}
	{\link{https://sf.net/p/tom7misc/svn/HEAD/tree/trunk/nand}}
\addpaper
	{HonestNN: an honest neural network "accelerator"}
	{Tim Linscott, Vidushi Goyal, Andrew McCrabb, and Pete Ehrett}
	{Keywords: accelerators, architecture, machine learning, ML, AI, DNN, CNN, graph processing, blockchain, cryptocurrency, 3D printing, security, crowdsourcing, computer, electronics, science, engineering, \#NovelResearch2019, \#BuzzwordsGetCites, \#BetterScience}
	{SIGBOVIK_2019_paper_8}
	{0cm}
	{\link[We can confirm that the authors were willing to part with a very nice bridge at a considerable discount.]{}}
\addpaper
	{Simultaneous microwaving architectures: An efficient scheme for multiplate heating}
	{Charles Yuan}
	{Keywords: high-energy physics, family and consumer sciences, computer architecture, dependent types, machine learning, Byzantine fault tolerance}
	{SIGBOVIK_2019_paper_22}
	{0cm}
	{}
\addpaper
	{Precise ECG platform on modern processors}
	{S.\@ Normalized Infloop and Ivybridge N.\@ Skylake}
	{Keywords: thermal systems, ambient heat modulating technologies, parallel heating, 2D computer graphics, edible content generation}
	{SIGBOVIK_2019_paper_33}
	{0cm}
	{}

\addtrack
	{}{Chess}
\addpaper
	{Is ``Dicong Qiu. Is this the shortest SIGBOVIK paper? From 2018 SIGBOVIK paper'' the shortest SIGBOVIK paper?}
	{Thomas Bach}
	{Keywords: o, o, o}
	{SIGBOVIK_2019_paper_14}
	{0cm}
	{}
\addpaper
	{Is this the tiniest SIGBOVIK paper ever?}
	{Mitchell Jones}
	{Keywords: tiny, zoom, Fermat}
	{SIGBOVIK_2019_paper_5}
	{0cm}
	{}
\addpaper
	{No, this is the tiniest SIGBOVIK paper ever.}
	{Patrick Lin}
	{Keywords: tony, zoom, Mitchell, heart}
	{SIGBOVIK_2019_paper_6}
	{0cm}
	{}
\addpaper
	{Revisiting the shortest SIGBOVIK paper / The revised shortest SIGBOVIK paper}
	{Richard Wardin}
	{Keywords: word golf, revisioned paper, deflation}
	{SIGBOVIK_2019_paper_9}
	{0cm}
	{}
\addreview{SIGBOVIK_2019_review_9}{0cm}

\addtrack
	{}{Simple in theory}
\addpaper
	{A sublinear approximation method for np-hardproblems on limited hardware}
	{Rohan Jhunjhunwala}
	{Keywords: P=NP, approximation methods, hardware}
	{SIGBOVIK_2019_paper_15}
	{0cm}
	{}
\addpaper
	{Simple theoretically practical complexity theory}
	{Ari Cohn}
	{Keywords: complexity theory, constant time, P vs. NP}
	{SIGBOVIK_2019_paper_27}
	{0cm}
	{}

\addtrack
	{}{Languages}
\addpaper
	{A formal semantics of Befunge}
	{Cameron Wong}
	{Keywords: Befunge, semantics, programming languages}
	{SIGBOVIK_2019_paper_24}
	{0cm}
	{}
\addpaper
	{LATEL: A Logical And Transparent Experimental Language}
	{Kelvin M.\@ Liu-Huang}
	{Keywords: conlang, constructed language, phonetics, morphosyntax, set theory, type theory, propositional logic}
	{SIGBOVIK_2019_paper_35}
	{0cm}
	{}
\addpaper
	{GullyNet: Our time will come}
	{Shuby Deshpande}
	{Keywords: AI, hip hop, protest}
	{SIGBOVIK_2019_paper_31}
	{0cm}
	{}

\addtrack
	{}{Error-correcting codes}
\addpaper
	{On double-sided QR codes}
	{Alexey Tikhonov}
	{Keywords: QR codes, steganography, error correction, high capacity, high density, robustness}
	{SIGBOVIK_2019_paper_2}
	{0cm}
	{}
\addreview{SIGBOVIK_2019_review_2}{0cm}
\addpaper
	{Novel defense against code theft using properties of Fibonacci series}
	{Sayan Chaudhry}
	{Keywords: indent, code style, Fibonacci, plagiarism}
	{SIGBOVIK_2019_paper_20}
	{0cm}
	{\link{https://github.com/shiftsayan/atom-fibonacci-indent}}
\addpaper
	{Error-detecting RLIRFO data structures for the win}
	{Darío de la Fuente García, Félix Áxel Gimeno Gil, and Juan Carlos Morales Vega}
	{Keywords: error detection, data structures, cosmic rays, stacks, stacks of stacks, stacks of stacks of stacks, template metaprogramming}
	{SIGBOVIK_2019_paper_25}
	{0cm}
	{}

\addtrack
	{}{Measurement studies}
\addpaper
	{Applications of Standard ML at Google}
	{Andrew Benson}
	{Keywords: SML, Standard ML, one-fifty, Harper, Google, software engineering, programming languages}
	{SIGBOVIK_2019_paper_19}
	{0cm}
	{}
\addpaper
	{93\% of paint splatters are valid Perl programs}
	{Colin McMillen and Tim Toady}
	{Keywords: perl, OCR, regret}
	{SIGBOVIK_2019_paper_34}
	{0cm}
	{\vspace{0.15in} {\scriptsize The authors assure us the materials will be available ``soon'' from: \url{http://famicol.in/sigbovik}} \raisebox{0in}{\includegraphics[height=0.75in]{participation}}}
\addpaper
	{A survey and projection of SIGBOVIK trends}
	{Jenny H. Lin}
	{Keywords: SIGBOVIK, self referential, ``Figures'', join the committee}
	{SIGBOVIK_2019_paper_chair}
	{0cm}
	{}

\addtrack
	{}{Back to the future}
\addpaper
	{Need more RAM? Just invent time travel!}
	{Robert Andrews, Mitchell Jones, Patrick Lin, and the UIUC Theory CS Group}
	{Keywords: complexity, Turing machine, time travel}
	{SIGBOVIK_2019_paper_23}
	{0cm}
	{}
\addpaper
	{WICCAN: (deep) learning directly from the future}
	{Amanda Coston and Alan Mishler}
	{Keywords: deep learning, data-free, dark arts}
	{SIGBOVIK_2019_paper_12}
	{0cm}
	{}
\addpaper
	{On CLI-based Renderers: In which we investigate the utility of rendering teapots in a command line}
	{Michael Sandler}
	{Keywords: teapot, render, speed and performance, command-line interface, CLI, graphics}
	{SIGBOVIK_2019_paper_40}
	{0cm}
	{}
\addpaper
	{SpaceF}
	{Oscar Hernandez and The Space Invaders}
	{Keywords: space, invasion, moonshot, government, \#yeswecandotherightthingandnotgotospace, extraterrestrial intelligence, National Rifle Association, cheese, George Mallary}
	{SIGBOVIK_2019_paper_30}
	{0cm}
	{}

\addtrack
	{}{Pop culture}
\addpaper
	{Which ITG stepcharts are bracket-jumpiest?: In which they milk the $\lceil$A boring follow-up paper to ``Which ITG stepcharts are turniest?'' titled, ``Which ITG stepcharts are crossoveriest and/or footswitchiest?''$\rfloor$ series for all its worth in publication count af}
	{Ben Blum}
	{Keywords: bracket, groove, in, jumps, submission title contains 289 characters which exceeds the maximum allowed length of 255 characters, the}
	{SIGBOVIK_2019_paper_29}
	{0cm}
	{\link[Their full results are posted at:]{https://tinyurl.com/bracketiest}}
\addpaper
	{The computational theory of Lord Voldemort's dark magic}
	{Huilian Sophie Qiu and Hui Yang}
	{Keywords: magic, computing, social good, green computing, Harry Potter, wizarding world, Lord Voldemort, flibbertigibbet}
	{SIGBOVIK_2019_paper_38}
	{0cm}
	{}
\addpaper
	{All you need is dogball}
	{Kai Arulkumaran, Matthew Kelcey, and Andrew Brock}
	{Keywords: dogball, biggan, memes}
	{SIGBOVIK_2019_paper_7}
	{0cm}
	{}
\addpaper
	{On the time complexity of the verification of the factorization of 2\textsuperscript{67}-1}
	{Isaac Grosof and Isaac Grosof}
	{Keywords: algorithms, time complexity, Mersenne prime, history of computation, multiplication}
	{SIGBOVIK_2019_paper_21}
	{0cm}
	{}

>>>>

\addtrack
	{TODO}{THERE CAN BE ONLY ONE}
\addpaper
	{Anonymous paper}
	{Anonymous Author}
	{Keywords: anonymous, triple blind, review}
	{SIGBOVIK_2020_paper_1}
	{0cm}
	{}
\addpaper
	{A polynomial-time SAT algorithm}
	{Anonymous Author(s)}
	{Keywords: theoretical computer science, complexity theory, p versus np}
	{SIGBOVIK_2020_paper_2}
	{0cm}
	{}
\addpaper
	{Visualizing player engagement with virtual spaces using GIS}
	{Frederick Chan}
	{Keywords: geographic information systems, virtual spaces, video games, video game anthropology}
	{SIGBOVIK_2020_paper_3}
	{0cm}
	{}
\addpaper
	{Determining the laziest way to force other people to generate random numbers for us using IoT vulnerabilities}
	{mathmasterzach, StarChar}
	{Keywords: babies, information theory, randomness, entropy, April fools, hacking, the law, coffee shops, smart-toasters}
	{SIGBOVIK_2020_paper_4}
	{0cm}
	{}
\addpaper
	{A disproof of the Theorem of Triviality}
	{Arul Kolla, August Deer, Ethan Kogan}
	{Keywords: theorem of triviality, theorem, meta problems, meta, math i guess}
	{SIGBOVIK_2020_paper_5}
	{0cm}
	{}
\addpaper
	{Image2image neural network for addition and subtraction evaluation of a pair of not very large numbers}
	{Vladimir Ivashkin}
	{Keywords: neural network, computer vision, calculator}
	% TODO
	{../message-from-committee}
	{0cm}
	{}
\addpaper
	{Faking ancient computer science:\@ A special SIGBOVIK tutorial}
	{Roxanne van der Pol, Brian van der Bijl, Diederik M.\@ Roijers}
	{Keywords: ancient computer science, aliens, conspiracy theories, Triangle of Conspiracy Succession, probability, Arcaicam Esperantom, random number generator, pseudo-science}
	{SIGBOVIK_2020_paper_7}
	{0cm}
	{}
\addpaper
	{Making explicit a constant appearing in an impossible equation of Carl and Moroz}
	{Matthew Weidner}
	{Keywords: computational mathematics, Hilbert's tenth problem, Diophantine sets}
	{SIGBOVIK_2020_paper_8}
	{0cm}
	{}
\addpaper
	{Can a paper be written entirely in the title? 1. Introduction: The title pretty much says it all. 2. Evaluation: It gets the job done. However, the title is a little long. 3. Conclusion: Yes.}
	{Daniel Gaston}
	{Keywords: innovation, strength, progress}
	{SIGBOVIK_2020_paper_9}
	{0cm}
	{}
\addpaper
	{RegisToken}
	{Irene Lin, Arnaud Avondet, Preston Vander Vos}
	{Keywords: blockchain, Ethereum, token, FCE, course registration}
	{SIGBOVIK_2020_paper_10}
	{0cm}
	{}
\addpaper
	{Erd\"os-Bacon-Sabbath numbers: \textit{Reductio ad absurdum}}
	{Maria Klawe \textit{et al.}\@ (incl.\@ Harry Q.\@ Bovik!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!1)}
	{Keywords: Paul Erd\"os, Kevin Bacon, Black Sabbath}
	% TODO
	{../message-from-committee}
	{0cm}
	{}
\addpaper
	{Formulating the syntactically simplest programming language}
	{Brendon Boldt}
	{Keywords: proramming languages, compilers, formal grammars}
	{SIGBOVIK_2020_paper_12}
	{0cm}
	{}
\addpaper
	{Training ImageNet in 1 second: Early stopping theoretical accelerate training}
	{Yiping Lu, Denny Wu}
	{Keywords: optimization, deep learning, machine learning theory}
	% TODO
	{../message-from-committee}
	{0cm}
	{}
\addpaper
	{Artificial general relativity}
	{Pablo Samuel Castro}
	{Keywords: physics, artificial, general relativity, quantum physics, universe-changing, new science, field equations, black holes}
	{SIGBOVIK_2020_paper_14}
	{0cm}
	{}
